Recursive algorithms, branching coefficients and applications

### 2010-10-01 AffineLieAlgebras/InformalNotes/article.tex
Lemma added

\documentclass[12pt]{iopart}
%\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{epstopdf}
%\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\newtheorem{statement}{Statement}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}

@@

\subsection{Proof of the recurrent relation}
\label{sec:proof}
\begin{theorem}
  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
  \begin{equation}
    \label{eq:1}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
  \begin{proof}
    Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
    projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
    \begin{equation*}
      % \label{eq:3}
      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
      \Longrightarrow\quad
      \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
    \end{equation*}
    The Weyl-Kac character formula leads to
    the relation
    \begin{equation}
      \label{eq:4}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
        {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
        e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
      {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
    \end{equation}

>>>>

\documentclass[12pt]{iopart}
%\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
%\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\newtheorem{statement}{Statement}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}

@@

\subsection{Proof of the recurrent relation}
\label{sec:proof}
First we prove the lemma
\begin{lemma}
Denote by $\mathcal{D}=\rho_{\af_{\bot}}-\pi_{\mathfrak{a}_{\bot}}\rho$ the difference between the Weyl vector of orthogonal subalgebra $\af_{\bot}$ and the projection of the Weyl vector of the algebra $\mathfrak{g}$. Then
the quotient of the singular weights element $\Psi^{(\mu)}$ by the denominator $R_{\af_{\bot}}$ is given by the formal element corresponding to the modified set of the singular weights of $L_{\af\oplus\mathfrak{h}_d}^{(\pi_{\af\oplus\mathfrak{h}_d}\mu)}$ with the multiplicities given by the dimensions of $\af_{\bot}$-modules.
\begin{equation*}
  \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\prod_{\alpha\in \Delta^{+}_{\bot}}\left(1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=
    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \mathrm{ch}_{\af_{\bot}}
      L^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}
\end{equation*}
\begin{proof}
  Consider $\Psi^{(\mu)}_{\mathfrak{g}}$. It is given by the sum over the Weyl group.
  \begin{equation*}
    \Psi^{(\mu)}_{\mathfrak{g}}=\sum_{w\in W}\epsilon(w)e^{w(\mu+\rho)-\rho}
  \end{equation*}
  We can divide the summation to the sum over $W_{\bot}$ and sum over all the classes of $W/W_{\bot}$: $w=vu,\; v\in W_{\bot},\; u \in W/W_{\bot}$. We have the following obvious property of the projections:
  \begin{equation*}
    \label{eq:5}
    u(\mu+\rho)=\pia(u(\mu+\rho))+\piab(u(\mu+\rho))+\pi_{(\mathfrak{h}\setminus
      (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}))^*}(u(\mu+\rho))
  \end{equation*}
  Let's denote $\mathfrak{h}\setminus (\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}})$ by $\mathfrak{h}_d$,
  $\mathfrak{h}=\mathfrak{h}_{\af}+\mathfrak{h}_{\af_{\bot}}+\mathfrak{h}_d$. Since $\mathfrak{h}_{\af}^*,\mathfrak{h}_d^*$ are invariant under the action of $v\in W_{\bot}$, we have
  \begin{equation*}
    \begin{array}{cc}
      vu(\mu+\rho)-\rho & = v\cdot(\piab(u(\mu+\rho))-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}+\\
      & \pia(u(\mu+\rho))-\rho+\rho_{\afb}+
      \pi_{\mathfrak{h}_d^*}(u(\mu+\rho))
    \end{array}
  \end{equation*}
 Only the first term depends on $v$. So
  \begin{equation*}
    \begin{array}{cc}
    \frac{\Psi^{(\mu)}_{\mathfrak{g}}}{\mathrm{R}_{\afb}}= &
    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pia(u(\mu+\rho))-\rho+\rho_{\afb}+\pi_{\mathfrak{h}_d^*}(u(\mu+\rho))}\cdot\\

    &\cdot\frac{
      \sum_{v\in W_{\bot}}\epsilon(v)e^{v(\piab u(\mu+\rho)-\rho_{\afb}+\rho_{\afb})-\rho_{\afb}}}{\mathrm{R}_{\afb}}
  \end{array}
\end{equation*}
  We can rewrite the r.h.s. as
  \begin{equation*}
    \sum_{u\in W/W_{\bot}}\epsilon(u)e^{\pi_{(\af\oplus\mathfrak{h}_d)}\left[u(\mu+\rho)-\rho\right]+\pi_{(\af\oplus \mathfrak{h}_d)}\cdot \rho-\rho+\rho_{\afb}}\cdot
    \mathrm{ch}_{\afb}L^{\pi_{\afb}u(\mu+\rho)-\rho_{\afb}}.
  \end{equation*}
  Since $\pi_{\afb}(u(\mu+\rho)-\rho)-(\rho_{\afb}-\pi_{\afb}\rho)=\pi_{\afb}(u(\mu+\rho)-\rho)-\mathcal{D}$ and $\pi_{(\af\oplus\mathfrak{h}_d)}\rho-\rho=-\pi_{\afb}\rho$ we get the statement of the Lemma.

\end{proof}
\end{lemma}

\begin{theorem}
  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
  \begin{equation}
    \label{eq:1}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
  \begin{proof}
    Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
    projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
    \begin{equation*}
      % \label{eq:3}
      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
      \Longrightarrow\quad
      \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
    \end{equation*}
    The Weyl-Kac character formula leads to
    the relation
    \begin{equation}
      \label{eq:4}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
        {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
        e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
      {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
    \end{equation}
